---
title: Effect of background noise on schroeder structure detection
subtitle: Fine scale acoustic perception in zebra finches
author: Marcelo Araya-Salas
date: "`r Sys.Date()`"
toc: true
toc-depth: 3
toc-location: left
number-sections: true
highlight-style: pygments
format:
  html:
    df-print: kable
    code-fold: true
    code-tools: true
    css: qmd.css
editor_options: 
  chunk_output_type: console
---

```{r add link to github repo, echo = FALSE, results='asis'}

# print link to github repo if any
if (file.exists("../.git/config")) {
  config <- readLines("../.git/config")
  url <- grep("url", config, value = TRUE)
  url <- gsub("\\turl = |.git$", "", url)
  cat("\nSource code and data found at [", url, "](", url, ")", sep = "")
}
.libPaths('/home/m/R/x86_64-pc-linux-gnu-library/4.5')
```

```{r load packages and setup style, echo = FALSE, message = FALSE, warning=FALSE}

# github packages must include user name ("user/package")
pkgs <- c("kableExtra", "knitr", "formatR", "seewave", "tuneR", "warbleR", "viridis", "Rraven", github = "maRce10/baRulho", "ggplot2", github = "maRce10/PhenotypeSpace", "ecodist", "numform")

# install/ load packages
sketchy::load_packages(pkgs, quite = TRUE)

# options to customize chunk outputs
knitr::opts_chunk$set(
  class.source = "numberLines lineAnchors", # for code line numbers
  tidy.opts = list(width.cutoff = 65),
  tidy = TRUE,
  message = FALSE
)

knitr::opts_knit$set(root.dir = "..")
```

&nbsp; 

<!-- skyblue box -->

<div class="alert alert-info">

# Purpose

- Evaluate the effect of degradation on the detection of acoustic fine structural variation in Schroeders

</div>

&nbsp;

```{r}

source("~/Dropbox/Projects/geographic_call_variation_yellow-naped_amazon/scripts/MRM2.R")

warbleR_options(parallel = 22)


```

# Data analysis workflow

```{mermaid}

flowchart LR
  A[Raw Schroeder\nrecordings] --> B(Aritfically\nDecrease SNR) 
  B --> C(measure\nSchroeder\nsimilarity)
  C --> D(Matrix\nregression\nmodels)
  
style A fill:#44015466
style B fill:#3E4A894D
style C fill:#6DCD594D
style D fill:#FDE7254D

```


# Degradation as a function of signal-to-noise ratio

- Adding synthetic noise to the master sound file annotations to decrease the signal-to-noise 
- Evaluate at which signal-to-noise ratio Schroeder sign can still be distinguished


## On 200ms schroeders

### Add synthetic noise

#### Repeated Schroeders
```{r, eval = FALSE}
master_annotations <- imp_raven(path = "./data/processed", files = "200ms_schroeders.txt", warbler.format = TRUE, all.data = TRUE)

master_annotations$sound.id <- paste0("f0:", master_annotations$f0, "_comp:", master_annotations$label)

master_annotations$sound.id[1] <- "start_marker"
master_annotations$sound.id[nrow(master_annotations)] <- "end_marker"

est_master <- selection_table(master_annotations[grep("marker", master_annotations$sound.id, invert = TRUE),], extended = TRUE, mar = 0.1, path = "./data/processed")


# est_schr <- readRDS("./data/processed/extended_selection_table_schroeders.RDS")
# est_schr <- readRDS(file.path(path, "extended_sel_table_degradation_exp.RDS"))
# est_schr$treatment <- ifelse(grepl("inside", est_schr$sound.files), "inside", "outside")
# est_schr$sound.id <- 1:nrow(est_schr)
# 
# est_in <- est_schr[est_schr$treatment == "inside", ]

est_master <- signal_to_noise_ratio(est_master, mar = 0.07, cores = 20)

hist(est_master$signal.to.noise.ratio)

adj_snr_schroeder_white <- lapply(30:1, function(i){
print(i)
    est_schr_adj <- baRulho::add_noise(X = est_master, target.snr = i, precision = 0.1, mar = 0.07, cores = 20, kind = "white", seed = NULL)
 est_schr_adj$target.snr <- i
 return(est_schr_adj)
})

beepr::beep(2)

saveRDS(adj_snr_schroeder_white, "./data/processed/200ms_schroeders_adjusted_snr_white_noise.RDS")
```

#### Single Schroders
```{r}
#| eval: false
#| 
est_schr <- readRDS("./data/processed/extended_selection_table_single_schroeders.RDS")

est_schr$sound.id <- "a"
est_schr <- signal_to_noise_ratio(X = est_schr, mar = 0.01, cores = 20, bp = NULL)

hist(est_schr$signal.to.noise.ratio)

adj_snr_schroeder_white <- lapply(30:1, function(i){
print(i)
    est_schr_adj <- add_noise(X = est_schr, target.snr = i, precision = 0.1, mar = 0.01, cores = 1, bp = NULL, kind = "white", seed = NULL)
 est_schr_adj$target.snr <- i
 return(est_schr_adj)
})

beepr::beep(2)

saveRDS(adj_snr_schroeder_white, "./data/processed/single_schroeder_adjusted_snr_white_noise.RDS")

```


### Check SNR adjusted waves

#### Examples

##### Repeated Schroeders
200 Hz, 9 components, positive phase
```{r}

adj_snr_schroeder <- readRDS("./data/processed/200ms_schroeders_adjusted_snr_white_noise.RDS")

# print(adj_snr_schroeder[[1]]$sound.id[10])

par(mar = c(0, 0, 0, 0), mfrow = c(5, 6))
for (i in 1:30){
    warbleR:::spectro_wrblr_int(
        wave = read_sound_file(adj_snr_schroeder[[i]], 10, from = 0, to = Inf),
        flim = c(0, 5),
        osc = FALSE,
        scale = FALSE,
        axisY = FALSE,
        axisX = FALSE,
        grid = FALSE,
        palette = viridis::mako,
        collevels = seq(-110, 0, 5)
    )
text(0.2, 4, paste("SNR:", adj_snr_schroeder[[i]]$target.snr[1]), col = "black", cex = 1.3)
    }
```

500 Hz, 16 components, positive phase
```{r}

# print(adj_snr_schroeder[[1]]$sound.id[150])

par(mar = c(0, 0, 0, 0), mfrow = c(5, 6))
for (i in 1:30){
    warbleR:::spectro_wrblr_int(
        wave = read_sound_file(adj_snr_schroeder[[i]], 150, from = 0, to = Inf),
        flim = c(0, 12),
        osc = FALSE,
        scale = FALSE,
        axisY = FALSE,
        axisX = FALSE,
        grid = FALSE,
        palette = viridis::mako,
        collevels = seq(-110, 0, 5)
    )
text(0.2, 11, paste("SNR:", adj_snr_schroeder[[i]]$target.snr[1]), col = "black", cex = 1.3)
    }
```

700 Hz, 24 components, positive phase
```{r}

# print(adj_snr_schroeder[[1]]$sound.id[250])

par(mar = c(0, 0, 0, 0), mfrow = c(5, 6))
for (i in 1:30){
    warbleR:::spectro_wrblr_int(
        wave = read_sound_file(adj_snr_schroeder[[i]], 250, from = 0, to = Inf),
        flim = c(0, 20),
        osc = FALSE,
        scale = FALSE,
        axisY = FALSE,
        axisX = FALSE,
        grid = FALSE,
        palette = viridis::mako,
        collevels = seq(-110, 0, 5)
    )
text(0.2, 18, paste("SNR:", adj_snr_schroeder[[i]]$target.snr[1]), col = "black", cex = 1.3)
    }
```

##### Single Schroeders
200 Hz, 9 components, positive phase
```{r}

adj_snr_schroeder <- readRDS("./data/processed/single_schroeder_adjusted_snr_white_noise.RDS")

# print(adj_snr_schroeder[[1]]$sound.id[10])

par(mar = c(0, 0, 0, 0), mfrow = c(5, 6))
for (i in 1:30){
   
    wv <- read_sound_file(adj_snr_schroeder[[i]], 10)@left
    
    plot(wv, type = "l", lwd = 2, col = mako(10)[6], xlab = "", ylab = "", axes = FALSE, ylim = c(-2, 2))
    box()
    
text(length(wv) / 2, 1.7, paste("SNR:", adj_snr_schroeder[[i]]$target.snr[1]), col = "black", cex = 1.3)
    }
```


200 Hz, 9 components, negative phase
```{r}

# print(adj_snr_schroeder[[1]]$sound.id[9])

par(mar = c(0, 0, 0, 0), mfrow = c(5, 6))
for (i in 1:30){
   
    wv <- read_sound_file(adj_snr_schroeder[[i]], 9)@left
    
    plot(wv, type = "l", lwd = 2, col = mako(10)[6], xlab = "", ylab = "", axes = FALSE, ylim = c(-2, 2))
    box()
    
text(length(wv) / 2, 1.7, paste("SNR:", adj_snr_schroeder[[i]]$target.snr[1]), col = "black", cex = 1.3)
    }
```

500 Hz, 16 components, positive phase
```{r}

# print(adj_snr_schroeder[[1]]$sound.files[150])

par(mar = c(0, 0, 0, 0), mfrow = c(5, 6))
for (i in 1:30){
   
    wv <- read_sound_file(adj_snr_schroeder[[i]], 150)@left
    
    plot(wv, type = "l", lwd = 2, col = mako(10)[6], xlab = "", ylab = "", axes = FALSE, ylim = c(-2, 2))
    box()
    
text(length(wv) / 2, 1.7, paste("SNR:", adj_snr_schroeder[[i]]$target.snr[1]), col = "black", cex = 1.3)
    }
```

500 Hz, 16 components, negative phase
```{r}

# print(adj_snr_schroeder[[1]]$sound.files[149])

par(mar = c(0, 0, 0, 0), mfrow = c(5, 6))
for (i in 1:30){
   
    wv <- read_sound_file(adj_snr_schroeder[[i]], 149)@left
    
    plot(wv, type = "l", lwd = 2, col = mako(10)[6], xlab = "", ylab = "", axes = FALSE, ylim = c(-2, 2))
    box()
    
text(length(wv) / 2, 1.7, paste("SNR:", adj_snr_schroeder[[i]]$target.snr[1]), col = "black", cex = 1.3)
    }
```

700 Hz, 24 components, positive phase
```{r}

# print(adj_snr_schroeder[[1]]$sound.files[250])

par(mar = c(0, 0, 0, 0), mfrow = c(5, 6))
for (i in 1:30){
   
    wv <- read_sound_file(adj_snr_schroeder[[i]], 250)@left
    
    plot(wv, type = "l", lwd = 2, col = mako(10)[6], xlab = "", ylab = "", axes = FALSE, ylim = c(-2, 2))
    box()
    
text(length(wv) / 2, 1.7, paste("SNR:", adj_snr_schroeder[[i]]$target.snr[1]), col = "black", cex = 1.3)
    }
```

700 Hz, 24 components, negative phase
```{r}

# print(adj_snr_schroeder[[1]]$sound.files[249])

par(mar = c(0, 0, 0, 0), mfrow = c(5, 6))
for (i in 1:30){
   
    wv <- read_sound_file(adj_snr_schroeder[[i]], 249)@left
    
    plot(wv, type = "l", lwd = 2, col = mako(10)[6], xlab = "", ylab = "", axes = FALSE, ylim = c(-2, 2))
    box()
    
text(length(wv) / 2, 1.7, paste("SNR:", adj_snr_schroeder[[i]]$target.snr[1]), col = "black", cex = 1.3)
    }
```
### Measure DTW distances
 
#### On repeated Schroeders
```{r, eval = FALSE}
adj_snr_schroeder <- readRDS("./data/processed/200ms_schroeders_adjusted_snr_white_noise.RDS")

dtw_dist_white_noise <- lapply(adj_snr_schroeder, function(schroeders) {

    print(schroeders$target.snr[1])
    cmbs <- t(combn(schroeders$sound.files, 2))

    min_dist_l <- pbapply::pbsapply(cl = 22, 1:nrow(cmbs), function(x) {
        s1 <- read_sound_file(schroeders, index = which(schroeders$sound.files ==
            cmbs[x, 1]))@left
        s2 <- read_sound_file(schroeders, index = which(schroeders$sound.files ==
            cmbs[x, 2]))@left

        # normalize
        s1 <- s1/max(abs(s1))
        s2 <- s2/max(abs(s2))

        # make same length if (length(s1) != length(s2))
        s1 <- approx(s1, n = 100)$y
        s2 <- approx(s2, n = 100)$y

        # duplicate 1
        s1 <- rep(s1, 2)

        # run dtw over longer vector
        dists <- vapply(seq_len(length(s1) - length(s2)), function(x) {
            segment <- s1[x:min(c(x + length(s2) - 1), length(s1))]

            dtw_dist <- dtw::dtwDist(mx = rbind(s2, segment))
            return(dtw_dist[1, 2])
        }, FUN.VALUE = numeric(1))

        return(data.frame(schr1 = cmbs[x, 1], schr2 = cmbs[x, 2],
            min(dists)))
    })

    min_dists <- do.call(rbind, min_dist_l)

    min_dists <- as.data.frame(matrix(min_dists[, 1], ncol = 3, byrow = TRUE))

    names(min_dists) <- c("schr1", "schr2", "dtw.dist")

    min_dists$dtw.dist <- as.numeric(min_dists$dtw.dist)

    min_dists$target.snr <- schroeders$target.snr[1]

    return(min_dists)

})

beepr::beep(2)

saveRDS(dtw_dist_white_noise, "./data/processed/dtw_distance_adjusted_snr_200ms_schroeders_white_noise.RDS")

```

#### On single Schroeders
```{r, eval = FALSE}
adj_snr_schroeder <- readRDS("./data/processed/single_schroeder_adjusted_snr_white_noise.RDS")

dtw_dist_white_noise <- lapply(adj_snr_schroeder, function(schroeders) {

    print(schroeders$target.snr[1])
    cmbs <- t(combn(schroeders$sound.files, 2))

    min_dist_l <- pbapply::pbsapply(cl = 22, 1:nrow(cmbs), function(x) {
        s1 <- read_sound_file(schroeders, index = which(schroeders$sound.files ==
            cmbs[x, 1]))@left
        s2 <- read_sound_file(schroeders, index = which(schroeders$sound.files ==
            cmbs[x, 2]))@left

        # normalize
        s1 <- s1/max(abs(s1))
        s2 <- s2/max(abs(s2))

        # make same length if (length(s1) != length(s2))
        s1 <- approx(s1, n = 100)$y
        s2 <- approx(s2, n = 100)$y

        # duplicate 1
        s1 <- rep(s1, 2)

        # run dtw over longer vector
        dists <- vapply(seq_len(length(s1) - length(s2)), function(x) {
            segment <- s1[x:min(c(x + length(s2) - 1), length(s1))]

            dtw_dist <- dtw::dtwDist(mx = rbind(s2, segment))
            return(dtw_dist[1, 2])
        }, FUN.VALUE = numeric(1))

        return(data.frame(schr1 = cmbs[x, 1], schr2 = cmbs[x, 2],
            min(dists)))
    })

    min_dists <- do.call(rbind, min_dist_l)

    min_dists <- as.data.frame(matrix(min_dists[, 1], ncol = 3, byrow = TRUE))

    names(min_dists) <- c("schr1", "schr2", "dtw.dist")

    min_dists$dtw.dist <- as.numeric(min_dists$dtw.dist)

    min_dists$target.snr <- schroeders$target.snr[1]

    return(min_dists)

})

beepr::beep(2)

saveRDS(dtw_dist_white_noise, "./data/processed/dtw_distance_adjusted_snr_single_schroeder_white_noise.RDS")

```


#### Statistical analysis

Modeling:
 - [Multiple Regression on distance Matrices](https://search.r-project.org/CRAN/refmans/ecodist/html/MRM.html) 
 - Model:   
 \begin{align*}
 Dissimilarity &\sim frequency + components + phase
 \end{align*}
 - Response values scaled to make effect sizes comparable across models
 - Predictors were coded as pairwise binary matrices in which 0 means that calls in a dyad belong to the same level and 1 means calls belong to different levels 
 - One model for each environment treatment as well as on the original model sounds

##### On repeated Schroeders
```{r, eval = FALSE}

dtw_dists_snr_list <-
    readRDS("./data/processed/dtw_distance_adjusted_snr_200ms_schroeders_white_noise.RDS")
    
adj_snr_schroeder1 <- readRDS("./data/processed/200ms_schroeders_adjusted_snr_white_noise.RDS")[[1]]

adj_snr_schroeder1$sound.id <- gsub("f0:f0 ", "f0:", adj_snr_schroeder1$sound.id)

    
dtw_wv_mod_list <-
    warbleR:::pblapply_wrblr_int(dtw_dists_snr_list, cl = 20, function(x) {
        
      # scale between 0 and 1
        x$dtw.dist <- (x$dtw.dist - min(x$dtw.dist)) / (max(x$dtw.dist) - min(x$dtw.dist))
        target_snr <- x$target.snr
        x$target.snr <- NULL
        
         
        x$schr1 <- sapply(x$schr1, function(x) adj_snr_schroeder1$sound.id[adj_snr_schroeder1$sound.files == x])
        x$schr2 <- sapply(x$schr2, function(x) adj_snr_schroeder1$sound.id[adj_snr_schroeder1$sound.files == x])
        
        dist_tri <- PhenotypeSpace::rectangular_to_triangular(x)
        
        freq_bi_tri <-
            as.dist(binary_triangular_matrix(group = sapply(strsplit(
                rownames(dist_tri), "_"
            ), "[[", 1)))
        
        comp_bi_tri <-
            as.dist(binary_triangular_matrix(group = gsub(
                "_n|_p", "", sapply(strsplit(rownames(dist_tri), "_"), "[[", 2)
            )))
        
        sign_bi_tri <-
            as.dist(binary_triangular_matrix(group = sapply(strsplit(
                rownames(dist_tri), "_"
            ), "[[", 3)))
        
        rect_var <-
            cbind(as.dist(dist_tri), freq_bi_tri, comp_bi_tri, sign_bi_tri)
        
        colnames(rect_var) <-
            c("dtw_dist", "frequency", "components", "sign")
        
        dtw_wv_mod <-
            MRM2(
                formula = dtw_dist ~ frequency + components + sign,
                nperm = 10000,
                mat = rect_var
            )
        
        return(dtw_wv_mod)
    })

names(dtw_wv_mod_list) <- paste0("snr:", sapply(dtw_dists_snr_list, function(x) x$target.snr[1]))

saveRDS(
    dtw_wv_mod_list,
    "./data/processed/matrix_correlation_dtw_distance_varying_snr_white_noise.RDS"
)


```

```{r, fig.cap = "Effect sizes by signal-to-noise ratio and predictor (color intensity shows effect size magnitude relative to the highest effect size within the model).", out.width="100%", fig.width=6, fig.height=4}
mods <- readRDS(
    "./data/processed/matrix_correlation_dtw_distance_varying_snr_white_noise.RDS"
)


estimates_dtw_wn <- do.call(rbind, lapply(seq_along(mods), function(x) {
  Y <- data.frame(mods[[x]]$coef[-1, ])
  # Y$rel_coef <- Y[, 1] / max(Y[, 1])
  Y$rel_coef <- Y[, 1] 
  Y$predictor <- rownames(Y)
  Y$model <- as.numeric(gsub("snr:", "", names(mods)[x]))
  names(Y) <- c("coef", "p", "rel_coef", "predictor", "model")
  return(Y)
}))

estimates_dtw_wn$rel_coef <- ifelse(estimates_dtw_wn$p < 0.05, estimates_dtw_wn$rel_coef, 0)
estimates_dtw_wn$signif <- ifelse(estimates_dtw_wn$p < 0.05, "p < 0.05", "p >= 0.05")
estimates_dtw_wn$signif2 <- ifelse(estimates_dtw_wn$p < 0.05, "*", "")

estimates_dtw_wn$model_f <- factor(estimates_dtw_wn$model, levels = 1:30)

ggplot(estimates_dtw_wn, aes(x = predictor, y = model_f, fill = rel_coef)) +
  geom_tile() +
  coord_equal() + 
    scale_fill_gradient2(
low = viridis(10)[3], high = viridis(10)[7],
    guide = "none"
  ) +
  geom_text(aes(label = signif2, color = signif), size = 3) +
  scale_color_manual(values = c("black", "gray"))+
    labs(y = "Signal-to-noise ratio", x = "Predictor", color = "P value") +
  theme_classic() +
  theme(axis.text.x = element_text(
    color = "black",
    size = 7, angle = 30, vjust = 0.8, hjust = 0.8
  )) + coord_flip()


estimates_dtw_wn$model <- as.numeric(estimates_dtw_wn$model)
```

```{r, fig.cap = "Effect sizes by signal-to-noise ratio and predictor.", out.width="100%"}

coef_by_signif <- aggregate(coef ~ signif, data = estimates_dtw_wn, FUN = range)

ggplot(estimates_dtw_wn, aes(y = coef, x = model, color = predictor, lty = predictor)) +
    geom_line(linewidth = 1.6) +
    labs(x = "Signal-to-noise ratio", y = "Effect size") + 
    scale_color_viridis_d(alpha = 0.7, begin = 0.2, end = 0.8) +
    geom_hline(yintercept = mean(coef_by_signif[,2][1, 1], coef_by_signif[,2][2, 2]), lty = 2, color = "gray") +
    theme_classic()

    
```

###### Only phase
```{r, fig.cap = "Effect sizes by signal-to-noise ratio and predictor.", out.width="100%"}
ggplot(estimates_dtw_wn[estimates_dtw_wn$predictor == "sign", ], aes(y = coef, x = model, color = predictor, lty = predictor)) +
    geom_line(linewidth = 1.6) +
    geom_smooth() +
    labs(x = "Signal-to-noise ratio", y = "Effect size") + 
    scale_color_viridis_d(alpha = 0.7, begin = 0.2, end = 0.8) +
    geom_hline(yintercept = mean(coef_by_signif[,2][1, 1], coef_by_signif[,2][2, 2]), lty = 2, color = "gray") +
    theme_classic()+
    geom_vline(xintercept = 16, lty = 2, color = "gray")


```

###### By frequency
```{r, eval = FALSE}

dtw_dists_snr_list <-
    readRDS("./data/processed/dtw_distance_adjusted_snr_200ms_schroeders_white_noise.RDS")
    
adj_snr_schroeder1 <- readRDS("./data/processed/200ms_schroeders_adjusted_snr_pink_noise.RDS")[[1]]

adj_snr_schroeder1$sound.id <- gsub("f0:f0 ", "f0:", adj_snr_schroeder1$sound.id)

dtw_wv_mod_list <-
    warbleR:::pblapply_wrblr_int(dtw_dists_snr_list, cl = 1, function(y) {
        
        # print(y$target.snr[1])
        freqs <- unique(substr(sapply(y[,1], function(x) adj_snr_schroeder1$sound.id[adj_snr_schroeder1$sound.files == x])
    , 0, 6))
        
        mods <- lapply(1:length(freqs), function(i){
            
            y$schr1 <- sapply(y$schr1, function(x) adj_snr_schroeder1$sound.id[adj_snr_schroeder1$sound.files == x])
            y$schr2 <- sapply(y$schr2, function(x) adj_snr_schroeder1$sound.id[adj_snr_schroeder1$sound.files == x])

            # extract only those with the same freq
            x <- y[grepl(paste(freqs[i], collapse = "|"), y$schr1) & grepl(paste(freqs[i], collapse = "|"), y$schr2),]
            
            target_snr <- x$target.snr
            x$target.snr <- NULL
            
            
            
            dist_tri <- PhenotypeSpace::rectangular_to_triangular(x)
            
            if (nrow(dist_tri) > 2){
                comp_bi_tri <-
                    as.dist(binary_triangular_matrix(group = gsub(
                        "_n|_p", "", sapply(strsplit(rownames(dist_tri), "_"), "[[", 2)
                    )))
                
                sign_bi_tri <-
                    as.dist(binary_triangular_matrix(group = sapply(strsplit(
                        rownames(dist_tri), "_"
                    ), "[[", 3)))
                
                rect_var <-
                    cbind(as.dist(dist_tri), comp_bi_tri, sign_bi_tri)
                
                colnames(rect_var) <-
                    c("dtw_dist", "components", "sign")
                
                dtw_wv_mod <-
                    MRM2(
                        formula = dtw_dist ~ components + sign,
                        nperm = 10000,
                        mat = rect_var
                    )
            } else 
                dtw_wv_mod <- NULL
            return(dtw_wv_mod) 
        })
        
        names(mods) <- paste0("snr:", y$target.snr[1], "_", freqs)
        
        mods <- mods[!sapply(mods, is.null)]        
        
        return(mods)
    })

saveRDS(
    dtw_wv_mod_list,
    "./data/processed/matrix_correlation_dtw_distance_varying_snr_by_frequency_white_noise.RDS"
)


```

Discriminating Schroeder's by phase grouped by frequency:
```{r, fig.cap = "Effect sizes for phase by signal-to-noise ratio and frequency.", out.width="100%"}
mods <- readRDS(
    "./data/processed/matrix_correlation_dtw_distance_varying_snr_by_frequency_white_noise.RDS"
)

estimates_list <- lapply(mods, function(y) {
    estimates <- do.call(rbind, lapply(seq_along(y), function(x) {
        Y <- data.frame(y[[x]]$coef[-1,])
        # Y$rel_coef <- Y[, 1] / max(Y[, 1])
        Y$rel_coef <- Y[, 1]
        Y$mod <- names(y)[x]
        Y$predictor <- rownames(Y)
        Y$freq <- strsplit(names(y)[x], "_")[[1]][2]
        Y$freq <- strsplit(Y$freq, ":")[[1]][2]
        names(Y) <- c("coef", "p", "rel_coef", "model", "predictor", "freq")
        Y$snr <- gsub("_", "", substr(names(y)[x], 0, 6))

        return(Y)
    }))
    
    estimates$rel_coef <-
        ifelse(estimates$p < 0.05, estimates$rel_coef, 0)
    estimates$signif <-
        ifelse(estimates$p < 0.05, "p < 0.05", "p >= 0.05")
    
    return(estimates)
})
estimates <- do.call(rbind, estimates_list)

estimates$snr <- as.numeric(substr(estimates$snr, 5, nchar(estimates$snr)))

rownames(estimates) <- 1:nrow(estimates)

coef_by_signif <- aggregate(coef ~ signif, data = estimates[estimates$predictor == "sign", ], FUN = range)

ggplot(estimates[estimates$predictor == "sign",], aes(y = coef, x = snr, color = freq)) +
    geom_line(linewidth = 1.6) +
    ylim(c(-0.2, 0.5)) +
    labs(x = "Signal-to-noise ratio", y = "Effect size when discriminating phase", color = "F0\nfrequency") + 
    scale_color_viridis_d(alpha = 0.7, begin = 0.2, end = 0.8) +
    theme_classic()

```

Discriminating Schroeder's by number of components grouped by frequency:
```{r, fig.cap = "Effect sizes for number of components by signal-to-noise ratio and frequency.", out.width="100%"}
coef_by_signif <- aggregate(coef ~ signif, data = estimates[estimates$predictor == "components", ], FUN = range)


ggplot(estimates[estimates$predictor == "components",], aes(y = coef, x = snr, color = freq)) +
    geom_line(linewidth = 1.6) +
    labs(x = "Signal-to-noise ratio", y = "Effect size when discriminating number of components", color = "F0\nfrequency") + 
    scale_color_viridis_d(alpha = 0.7, begin = 0.1, end = 0.9) +
    geom_hline(yintercept = mean(coef_by_signif[,2][1, 1], coef_by_signif[,2][2, 2]), lty = 2, color = "gray") +
    theme_classic()

```

##### On single Schroeders
```{r, eval = FALSE}

dtw_dists_snr_list <-
    readRDS("./data/processed/dtw_distance_adjusted_snr_single_schroeder_white_noise.RDS")
    
adj_snr_schroeder1 <- readRDS("./data/processed/200ms_schroeders_adjusted_snr_white_noise.RDS")[[1]]

adj_snr_schroeder1$sound.id <- gsub("f0:f0 ", "f0:", adj_snr_schroeder1$sound.id)

    
dtw_wv_mod_list <-
    warbleR:::pblapply_wrblr_int(dtw_dists_snr_list, cl = 20, function(x) {
        
        # scale within a 0-1 range
        x$dtw.dist <- (x$dtw.dist - min(x$dtw.dist)) / (max(x$dtw.dist) - min(x$dtw.dist))
        
        target_snr <- x$target.snr
        x$target.snr <- NULL
        
        x$schr1 <- sapply(strsplit(x$schr1, "_"), function(x) paste(x[2], x[3], substr(x[4], 0, 1),sep = "_"))
        x$schr2 <- sapply(strsplit(x$schr2, "_"), function(x) paste(x[2], x[3], substr(x[4], 0, 1),sep = "_"))
         
        # x$schr1 <- sapply(x$schr1, function(x) adj_snr_schroeder1$sound.id[adj_snr_schroeder1$sound.files == x])
        # x$schr2 <- sapply(x$schr2, function(x) adj_snr_schroeder1$sound.id[adj_snr_schroeder1$sound.files == x])
        # 
        dist_tri <- PhenotypeSpace::rectangular_to_triangular(x)
        
        freq_bi_tri <-
            as.dist(binary_triangular_matrix(group = sapply(strsplit(
                rownames(dist_tri), "_"
            ), "[[", 1)))
        
        comp_bi_tri <-
            as.dist(binary_triangular_matrix(group = gsub(
                "_n|_p", "", sapply(strsplit(rownames(dist_tri), "_"), "[[", 2)
            )))
        
        sign_bi_tri <-
            as.dist(binary_triangular_matrix(group = sapply(strsplit(
                rownames(dist_tri), "_"
            ), "[[", 3)))
        
        rect_var <-
            cbind(as.dist(dist_tri), freq_bi_tri, comp_bi_tri, sign_bi_tri)
        
        colnames(rect_var) <-
            c("dtw_dist", "frequency", "components", "sign")
        
        dtw_wv_mod <-
            MRM2(
                formula = dtw_dist ~ frequency + components + sign,
                nperm = 10000,
                mat = rect_var
            )
        
        return(dtw_wv_mod)
    })

names(dtw_wv_mod_list) <- paste0("snr:", sapply(dtw_dists_snr_list, function(x) x$target.snr[1]))

saveRDS(
    dtw_wv_mod_list,
    "./data/processed/matrix_correlation_dtw_distance_single_schroeder_varying_snr_white_noise.RDS"
)


```

```{r, fig.cap = "Effect sizes by signal-to-noise ratio and predictor (color intensity shows effect size magnitude relative to the highest effect size within the model).", out.width="100%", fig.width=6, fig.height=4}
mods <- readRDS(
    "./data/processed/matrix_correlation_dtw_distance_single_schroeder_varying_snr_white_noise.RDS"
)


estimates_dtw_wn_stnd <- do.call(rbind, lapply(seq_along(mods), function(x) {
  Y <- data.frame(mods[[x]]$coef[-1, ])
  # Y$rel_coef <- Y[, 1] / max(Y[, 1])
  Y$rel_coef <- Y[, 1] 
  Y$predictor <- rownames(Y)
  Y$model <- as.numeric(gsub("snr:", "", names(mods)[x]))
  names(Y) <- c("coef", "p", "rel_coef", "predictor", "model")
  return(Y)
}))

estimates_dtw_wn_stnd$rel_coef <- ifelse(estimates_dtw_wn_stnd$p < 0.05, estimates_dtw_wn_stnd$rel_coef, 0)
estimates_dtw_wn_stnd$signif <- ifelse(estimates_dtw_wn_stnd$p < 0.05, "p < 0.05", "p >= 0.05")
estimates_dtw_wn_stnd$signif2 <- ifelse(estimates_dtw_wn_stnd$p < 0.05, "*", "")

estimates_dtw_wn_stnd$model_f <- factor(estimates_dtw_wn_stnd$model, levels = 1:30)

ggplot(estimates_dtw_wn_stnd, aes(x = predictor, y = model_f, fill = rel_coef)) +
  geom_tile() +
  coord_equal() + 
    scale_fill_gradient2(
low = viridis(10)[3], high = viridis(10)[7],
    guide = "none"
  ) +
  geom_text(aes(label = signif2, color = signif), size = 3) +
  scale_color_manual(values = c("black", "gray"))+
    labs(y = "Signal-to-noise ratio", x = "Predictor", color = "P value") +
  theme_classic() +
  theme(axis.text.x = element_text(
    color = "black",
    size = 7, angle = 30, vjust = 0.8, hjust = 0.8
  )) + coord_flip()


estimates_dtw_wn_stnd$model <- as.numeric(estimates_dtw_wn_stnd$model)
```

```{r, fig.cap = "Effect sizes by signal-to-noise ratio and predictor.", out.width="100%"}

coef_by_signif <- aggregate(coef ~ signif, data = estimates_dtw_wn_stnd, FUN = range)

ggplot(estimates_dtw_wn_stnd, aes(y = coef, x = model, color = predictor, lty = predictor)) +
    geom_line(linewidth = 1.6) +
    labs(x = "Signal-to-noise ratio", y = "Effect size") + 
    scale_color_viridis_d(alpha = 0.7, begin = 0.2, end = 0.8) +
    geom_hline(yintercept = mean(coef_by_signif[,2][1, 1], coef_by_signif[,2][2, 2]), lty = 2, color = "gray") +
    theme_classic()

    
```

###### Only phase
```{r, fig.cap = "Effect sizes by signal-to-noise ratio and predictor.", out.width="100%"}
ggplot(estimates_dtw_wn_stnd[estimates_dtw_wn_stnd$predictor == "sign", ], aes(y = coef, x = model, color = predictor, lty = predictor)) +
    geom_line(linewidth = 1.6) +
    geom_smooth() +
    labs(x = "Signal-to-noise ratio", y = "Effect size") + 
    scale_color_viridis_d(alpha = 0.7, begin = 0.2, end = 0.8) +
    geom_hline(yintercept = mean(coef_by_signif[,2][1, 1], coef_by_signif[,2][2, 2]), lty = 2, color = "gray") +
    theme_classic()+
    geom_vline(xintercept = 16, lty = 2, color = "gray")


```

###### By frequency
```{r, eval = FALSE}

dtw_dists_snr_list <-
    readRDS("./data/processed/dtw_distance_adjusted_snr_200ms_schroeders_white_noise.RDS")
    
adj_snr_schroeder1 <- readRDS("./data/processed/200ms_schroeders_adjusted_snr_pink_noise.RDS")[[1]]

adj_snr_schroeder1$sound.id <- gsub("f0:f0 ", "f0:", adj_snr_schroeder1$sound.id)

dtw_wv_mod_list <-
    warbleR:::pblapply_wrblr_int(dtw_dists_snr_list, cl = 1, function(y) {
        
        # print(y$target.snr[1])
        freqs <- unique(substr(sapply(y[,1], function(x) adj_snr_schroeder1$sound.id[adj_snr_schroeder1$sound.files == x])
    , 0, 6))
        
        mods <- lapply(1:length(freqs), function(i){
            
            y$schr1 <- sapply(y$schr1, function(x) adj_snr_schroeder1$sound.id[adj_snr_schroeder1$sound.files == x])
            y$schr2 <- sapply(y$schr2, function(x) adj_snr_schroeder1$sound.id[adj_snr_schroeder1$sound.files == x])

            # extract only those with the same freq
            x <- y[grepl(paste(freqs[i], collapse = "|"), y$schr1) & grepl(paste(freqs[i], collapse = "|"), y$schr2),]
            
            target_snr <- x$target.snr
            x$target.snr <- NULL
            
            
            
            dist_tri <- PhenotypeSpace::rectangular_to_triangular(x)
            
            if (nrow(dist_tri) > 2){
                comp_bi_tri <-
                    as.dist(binary_triangular_matrix(group = gsub(
                        "_n|_p", "", sapply(strsplit(rownames(dist_tri), "_"), "[[", 2)
                    )))
                
                sign_bi_tri <-
                    as.dist(binary_triangular_matrix(group = sapply(strsplit(
                        rownames(dist_tri), "_"
                    ), "[[", 3)))
                
                rect_var <-
                    cbind(as.dist(dist_tri), comp_bi_tri, sign_bi_tri)
                
                colnames(rect_var) <-
                    c("dtw_dist", "components", "sign")
                
                dtw_wv_mod <-
                    MRM2(
                        formula = dtw_dist ~ components + sign,
                        nperm = 10000,
                        mat = rect_var
                    )
            } else 
                dtw_wv_mod <- NULL
            return(dtw_wv_mod) 
        })
        
        names(mods) <- paste0("snr:", y$target.snr[1], "_", freqs)
        
        mods <- mods[!sapply(mods, is.null)]        
        
        return(mods)
    })

saveRDS(
    dtw_wv_mod_list,
    "./data/processed/matrix_correlation_dtw_distance_varying_snr_by_frequency_white_noise.RDS"
)


```

Discriminating Schroeder's by phase grouped by frequency:
```{r, fig.cap = "Effect sizes for phase by signal-to-noise ratio and frequency.", out.width="100%"}
mods <- readRDS(
    "./data/processed/matrix_correlation_dtw_distance_varying_snr_by_frequency_white_noise.RDS"
)

estimates_list <- lapply(mods, function(y) {
    estimates <- do.call(rbind, lapply(seq_along(y), function(x) {
        Y <- data.frame(y[[x]]$coef[-1,])
        # Y$rel_coef <- Y[, 1] / max(Y[, 1])
        Y$rel_coef <- Y[, 1]
        Y$mod <- names(y)[x]
        Y$predictor <- rownames(Y)
        Y$freq <- strsplit(names(y)[x], "_")[[1]][2]
        Y$freq <- strsplit(Y$freq, ":")[[1]][2]
        names(Y) <- c("coef", "p", "rel_coef", "model", "predictor", "freq")
        Y$snr <- gsub("_", "", substr(names(y)[x], 0, 6))

        return(Y)
    }))
    
    estimates$rel_coef <-
        ifelse(estimates$p < 0.05, estimates$rel_coef, 0)
    estimates$signif <-
        ifelse(estimates$p < 0.05, "p < 0.05", "p >= 0.05")
    
    return(estimates)
})
estimates <- do.call(rbind, estimates_list)

estimates$snr <- as.numeric(substr(estimates$snr, 5, nchar(estimates$snr)))

rownames(estimates) <- 1:nrow(estimates)

coef_by_signif <- aggregate(coef ~ signif, data = estimates[estimates$predictor == "sign", ], FUN = range)

ggplot(estimates[estimates$predictor == "sign",], aes(y = coef, x = snr, color = freq)) +
    geom_line(linewidth = 1.6) +
    ylim(c(-0.2, 0.5)) +
    labs(x = "Signal-to-noise ratio", y = "Effect size when discriminating phase", color = "F0\nfrequency") + 
    scale_color_viridis_d(alpha = 0.7, begin = 0.2, end = 0.8) +
    theme_classic()

```

Discriminating Schroeder's by number of components grouped by frequency:
```{r, fig.cap = "Effect sizes for number of components by signal-to-noise ratio and frequency.", out.width="100%"}
coef_by_signif <- aggregate(coef ~ signif, data = estimates[estimates$predictor == "components", ], FUN = range)


ggplot(estimates[estimates$predictor == "components",], aes(y = coef, x = snr, color = freq)) +
    geom_line(linewidth = 1.6) +
    labs(x = "Signal-to-noise ratio", y = "Effect size when discriminating number of components", color = "F0\nfrequency") + 
    scale_color_viridis_d(alpha = 0.7, begin = 0.1, end = 0.9) +
    geom_hline(yintercept = mean(coef_by_signif[,2][1, 1], coef_by_signif[,2][2, 2]), lty = 2, color = "gray") +
    theme_classic()

```

### Measure waveform correlation

#### On repeated Schroeders
```{r, eval = FALSE}

adj_snr_schroeder <- readRDS("./data/processed/200ms_schroeders_adjusted_snr_white_noise.RDS")

cor_noise <- lapply(adj_snr_schroeder, function(schroeders) {

    print(schroeders$target.snr[1])
    cmbs <- t(combn(schroeders$sound.files, 2))


min_cor_l <- pbapply::pbsapply(cl = 20, 1:nrow(cmbs), function(x) {
  s1 <- read_sound_file(schroeders, index = which(schroeders$sound.files == cmbs[x, 1]))@left
 s2 <- read_sound_file(schroeders, index = which(schroeders$sound.files == cmbs[x, 2]))@left

 # normalize
 s1 <- s1 / max(abs(s1))
 s2 <- s2 / max(abs(s2))
 
  # make same length
  # if (length(s1) != length(s2))
  s1 <- approx(s1, n = 100)$y
  s2 <- approx(s2, n = 100)$y

 # run correlation
  cor <- cor(s1, s2)

  return(data.frame(schr1 = cmbs[x, 1], schr2 = cmbs[x, 2], cor = cor))

})

cors <- do.call(rbind, min_cor_l)

cors <- as.data.frame(matrix(cors[, 1], ncol = 3, byrow = TRUE))

names(cors) <- c("schr1", "schr2", "cor")

cors$cor <- as.numeric(cors$cor)


cors$target.snr <- cors$target.snr[1]    

    return(cors)

})

names(cor_noise) <- paste0("snr:", sapply(adj_snr_schroeder, function(x) x$target.snr[1]))


beepr::beep(2)

saveRDS(cor_noise, "./data/processed/waveform_correlation_adjusted_snr_200ms_schroeders_white_noise.RDS")
```

#### On single Schroeders
```{r, eval = FALSE}

adj_snr_schroeder <- readRDS("./data/processed/single_schroeder_adjusted_snr_white_noise.RDS")

cor_noise <- lapply(adj_snr_schroeder, function(schroeders) {

    print(schroeders$target.snr[1])
    cmbs <- t(combn(schroeders$sound.files, 2))


min_cor_l <- pbapply::pbsapply(cl = 20, 1:nrow(cmbs), function(x) {
  s1 <- read_sound_file(schroeders, index = which(schroeders$sound.files == cmbs[x, 1]))@left
 s2 <- read_sound_file(schroeders, index = which(schroeders$sound.files == cmbs[x, 2]))@left

 # normalize
 s1 <- s1 / max(abs(s1))
 s2 <- s2 / max(abs(s2))
 
  # make same length
  # if (length(s1) != length(s2))
  s1 <- approx(s1, n = 100)$y
  s2 <- approx(s2, n = 100)$y

 # run correlation
  cor <- cor(s1, s2)

  return(data.frame(schr1 = cmbs[x, 1], schr2 = cmbs[x, 2], cor = cor))

})

cors <- do.call(rbind, min_cor_l)

cors <- as.data.frame(matrix(cors[, 1], ncol = 3, byrow = TRUE))

names(cors) <- c("schr1", "schr2", "cor")

cors$cor <- as.numeric(cors$cor)


cors$target.snr <- cors$target.snr[1]    

    return(cors)

})

names(cor_noise) <- paste0("snr:", sapply(adj_snr_schroeder, function(x) x$target.snr[1]))


beepr::beep(2)

saveRDS(cor_noise, "./data/processed/waveform_correlation_adjusted_snr_single_schroeders_white_noise.RDS")
```

#### Statistical analysis

##### On repeated Schroeders
```{r, eval = FALSE}

cor_snr_list <-
    readRDS("./data/processed/waveform_correlation_adjusted_snr_200ms_schroeders_white_noise.RDS")
    
adj_snr_schroeder1 <- readRDS("./data/processed/200ms_schroeders_adjusted_snr_white_noise.RDS")[[1]]

adj_snr_schroeder1$sound.id <- gsub("f0:f0 ", "f0:", adj_snr_schroeder1$sound.id)

    
cor_mod_list <-
    warbleR:::pblapply_wrblr_int(names(cor_snr_list), cl = 20, function(x) {
        
        x <- cor_snr_list[[x]]
        # x$dist <- scale(x$dist)
        target_snr <- "snr:30"
        
         
        x$schr1 <- sapply(x$schr1, function(x) adj_snr_schroeder1$sound.id[adj_snr_schroeder1$sound.files == x])
        x$schr2 <- sapply(x$schr2, function(x) adj_snr_schroeder1$sound.id[adj_snr_schroeder1$sound.files == x])
        x$cor <- x$cor * -1
        
        dist_tri <- PhenotypeSpace::rectangular_to_triangular(x)
        
        freq_bi_tri <-
            as.dist(binary_triangular_matrix(group = sapply(strsplit(
                rownames(dist_tri), "_"
            ), "[[", 1)))
        
        comp_bi_tri <-
            as.dist(binary_triangular_matrix(group = gsub(
                "_n|_p", "", sapply(strsplit(rownames(dist_tri), "_"), "[[", 2)
            )))
        
        sign_bi_tri <-
            as.dist(binary_triangular_matrix(group = sapply(strsplit(
                rownames(dist_tri), "_"
            ), "[[", 3)))
        
        rect_var <-
            cbind(as.dist(dist_tri), freq_bi_tri, comp_bi_tri, sign_bi_tri)
        
        colnames(rect_var) <-
            c("cor", "frequency", "components", "sign")
        
        cor_wv_mod <-
            MRM2(
                formula = cor ~ frequency + components + sign,
                nperm = 10000,
                mat = rect_var
            )
        
        return(cor_wv_mod)
    })

names(cor_mod_list) <- names(cor_snr_list)

saveRDS(
    cor_mod_list,
    "./data/processed/matrix_regression_waveform_correlation_varying_snr_white_noise.RDS"
)

```

```{r, fig.cap = "Effect sizes by signal-to-noise ratio and predictor (color intensity shows effect size magnitude relative to the highest effect size within the model).", out.width="100%", fig.width=6, fig.height=4}

mods <- readRDS(
    "./data/processed/matrix_regression_waveform_correlation_varying_snr_white_noise.RDS"
)

estimates_wf_wn <- do.call(rbind, lapply(seq_along(mods), function(x) {
  Y <- data.frame(mods[[x]]$coef[-1, ])
  # Y$rel_coef <- Y[, 1] / max(Y[, 1])
  Y$rel_coef <- Y[, 1] 
  Y$predictor <- rownames(Y)
  Y$model <- as.numeric(gsub("snr:", "", names(mods)[x]))
  names(Y) <- c("coef", "p", "rel_coef", "predictor", "model")
  return(Y)
}))

estimates_wf_wn$rel_coef <- ifelse(estimates_wf_wn$p < 0.05, estimates_wf_wn$rel_coef, 0)
estimates_wf_wn$signif <- ifelse(estimates_wf_wn$p < 0.05, "p < 0.05", "p >= 0.05")
estimates_wf_wn$signif2 <- ifelse(estimates_wf_wn$p < 0.05, "*", "")

estimates_wf_wn$model_f <- factor(estimates_wf_wn$model, levels = 1:30)

ggplot(estimates_wf_wn, aes(x = predictor, y = model_f, fill = rel_coef)) +
  geom_tile() +
  coord_equal() + 
    scale_fill_gradient2(
low = viridis(10)[3], high = viridis(10)[7],
    guide = "none"
  ) +
  geom_text(aes(label = signif2, color = signif), size = 3) +
  scale_color_manual(values = c("black", "gray"))+
    labs(y = "Signal-to-noise ratio", x = "Predictor", color = "P value") +
  theme_classic() +
  theme(axis.text.x = element_text(
    color = "black",
    size = 7, angle = 30, vjust = 0.8, hjust = 0.8
  )) + coord_flip()


estimates_wf_wn$model <- as.numeric(estimates_wf_wn$model)
```

```{r, fig.cap = "Effect sizes by signal-to-noise ratio and predictor waveform correlation", out.width="100%"}

coef_by_signif <- aggregate(coef ~ signif, data = estimates_wf_wn, FUN = range)

ggplot(estimates_wf_wn, aes(y = coef, x = model, color = predictor, lty = predictor)) +
    geom_line(linewidth = 1.6) +
    labs(x = "Signal-to-noise ratio", y = "Effect size") + 
    scale_color_viridis_d(alpha = 0.7, begin = 0.2, end = 0.8) +
    geom_hline(yintercept = mean(coef_by_signif[,2][1, 1], coef_by_signif[,2][2, 2]), lty = 2, color = "gray") +
    theme_classic()

    
```

###### Only phase
```{r, fig.cap = "Effect sizes by signal-to-noise ratio and predictor waveform correlation.", out.width="100%"}
ggplot(estimates_wf_wn[estimates_wf_wn$predictor == "sign", ], aes(y = coef, x = model, color = predictor, lty = predictor)) +
    geom_line(linewidth = 1.6) +
    geom_smooth() +
    labs(x = "Signal-to-noise ratio", y = "Effect size") + 
    scale_color_viridis_d(alpha = 0.7, begin = 0.2, end = 0.8) +
    geom_hline(yintercept = mean(coef_by_signif[,2][1, 1], coef_by_signif[,2][2, 2]), lty = 2, color = "gray") +
    theme_classic() + 
    geom_vline(xintercept = 2, lty = 2, color = "gray")


```

###### By frequency
```{r, eval = FALSE}

cor_snr_list <-
    readRDS(
            "./data/processed/waveform_correlation_adjusted_snr_200ms_schroeders_white_noise.RDS"
        )
adj_snr_schroeder1 <- readRDS("./data/processed/200ms_schroeders_adjusted_snr_pink_noise.RDS")[[1]]


cor_snr_list <- lapply(seq_along(cor_snr_list), function(x) {
    Y <- cor_snr_list[[x]]
    Y$target.snr <- gsub("snr:", "", names(cor_snr_list)[x])
    return(Y)
    })

adj_snr_schroeder1$sound.id <- gsub("f0:f0 ", "f0:", adj_snr_schroeder1$sound.id)

cor_mod_list <-
    warbleR:::pblapply_wrblr_int(cor_snr_list, cl = 1, function(y) {
        
        freqs <- unique(substr(sapply(y[,1], function(x) adj_snr_schroeder1$sound.id[adj_snr_schroeder1$sound.files == x])
    , 0, 6))

        mods <- lapply(1:length(freqs), function(i){
            
            y$schr1 <- sapply(y$schr1, function(x) adj_snr_schroeder1$sound.id[adj_snr_schroeder1$sound.files == x])
            y$schr2 <- sapply(y$schr2, function(x) adj_snr_schroeder1$sound.id[adj_snr_schroeder1$sound.files == x])

            
            # extract only those with the same freq
            x <- y[grepl(paste(freqs[i], collapse = "|"), y$schr1) & grepl(paste(freqs[i], collapse = "|"), y$schr2),]
            
            target_snr <- x$target.snr
            x$target.snr <- NULL
            x$cor <- 1- x$cor
            
            dist_tri <- PhenotypeSpace::rectangular_to_triangular(x)
            
            if (nrow(dist_tri) > 2){
                comp_bi_tri <-
                    as.dist(binary_triangular_matrix(group = gsub(
                        "_n|_p", "", sapply(strsplit(rownames(dist_tri), "_"), "[[", 2)
                    )))
                
                sign_bi_tri <-
                    as.dist(binary_triangular_matrix(group = sapply(strsplit(
                        rownames(dist_tri), "_"
                    ), "[[", 3)))
                
                rect_var <-
                    cbind(as.dist(dist_tri), comp_bi_tri, sign_bi_tri)
                
                colnames(rect_var) <-
                    c("dtw_dist", "components", "sign")
                
                cor_mod <-
                    MRM2(
                        formula = dtw_dist ~ components + sign,
                        nperm = 10000,
                        mat = rect_var
                    )
            } else 
                cor_mod <- NULL
            return(cor_mod) 
        })
        
        names(mods) <- paste0("snr:", y$target.snr[1], "_", freqs)
        
        mods <- mods[!sapply(mods, is.null)]        
        
        return(mods)
    })

saveRDS(
    cor_mod_list,
    "./data/processed/matrix_correlation_waveforme_correlatione_varying_snr_by_frequency_white_noise.RDS"
)

```

Discriminating Schroeder's by phase grouped by frequency:
```{r, fig.cap = "Effect sizes for phase by signal-to-noise ratio and frequency.", out.width="100%"}
mods <- readRDS(
    "./data/processed/matrix_correlation_waveforme_correlatione_varying_snr_by_frequency_white_noise.RDS"
)

estimates_list <- lapply(mods, function(y) {
    estimates <- do.call(rbind, lapply(seq_along(y), function(x) {
        Y <- data.frame(y[[x]]$coef[-1,])
        # Y$rel_coef <- Y[, 1] / max(Y[, 1])
        Y$rel_coef <- Y[, 1]
        Y$mod <- names(y)[x]
        Y$predictor <- rownames(Y)
        Y$freq <- strsplit(names(y)[x], "_")[[1]][2]
        Y$freq <- strsplit(Y$freq, ":")[[1]][2]
        names(Y) <- c("coef", "p", "rel_coef", "model", "predictor", "freq")
        Y$snr <- gsub("_", "", substr(names(y)[x], 0, 6))

        return(Y)
    }))
    
    estimates$rel_coef <-
        ifelse(estimates$p < 0.05, estimates$rel_coef, 0)
    estimates$signif <-
        ifelse(estimates$p < 0.05, "p < 0.05", "p >= 0.05")
    
    return(estimates)
})
estimates <- do.call(rbind, estimates_list)

estimates$snr <- as.numeric(substr(estimates$snr, 5, nchar(estimates$snr)))

rownames(estimates) <- 1:nrow(estimates)

coef_by_signif <- aggregate(coef ~ signif, data = estimates[estimates$predictor == "sign", ], FUN = range)

ggplot(estimates[estimates$predictor == "sign",], aes(y = coef, x = snr, color = freq)) +
    geom_line(linewidth = 1.6) +
    labs(x = "Signal-to-noise ratio", y = "Effect size when discriminating phase", color = "F0\nfrequency") + 
    scale_color_viridis_d(alpha = 0.7, begin = 0.2, end = 0.8) +
    theme_classic()

```

Discriminating Schroeder's by number of components grouped by frequency:
```{r, fig.cap = "Effect sizes for number of components by signal-to-noise ratio and frequency.", out.width="100%"}
coef_by_signif <- aggregate(coef ~ signif, data = estimates[estimates$predictor == "components", ], FUN = range)


ggplot(estimates[estimates$predictor == "components",], aes(y = coef, x = snr, color = freq)) +
    geom_line(linewidth = 1.6) +
    labs(x = "Signal-to-noise ratio", y = "Effect size when discriminating number of components", color = "F0\nfrequency") + 
    scale_color_viridis_d(alpha = 0.7, begin = 0.2, end = 0.8) +
    geom_hline(yintercept = mean(coef_by_signif[,2][1, 1], coef_by_signif[,2][2, 2]), lty = 2, color = "gray") +
    theme_classic()

```

###### By component
```{r, eval = FALSE}


dtw_dists_snr_list <-
    readRDS(
            "./data/processed/dtw_distance_schroeders_degradation_experiment_varying_snr.RDS"
        )
    

dtw_wv_mod_list <-
    warbleR:::pblapply_wrblr_int(dtw_dists_snr_list, cl = 1, function(y) {
        
        # print(y$target.snr[1])
        comps <- unique(sapply(strsplit(y[,1], "_"),"[[", 2))
        
        mods <- lapply(1:length(comps), function(i){
            
            # extract only those with the same freq
            x <- y[grepl(paste(comps[i], collapse = "|"), y$schr1) & grepl(paste(comps[i], collapse = "|"), y$schr2), ]
            
            target_snr <- x$target.snr
            x$target.snr <- NULL
            
            dist_tri <- PhenotypeSpace::rectangular_to_triangular(x)
            
            if (nrow(dist_tri) > 2){
                
                 freq_bi_tri <-
            as.dist(binary_triangular_matrix(group = sapply(strsplit(
                rownames(dist_tri), "_"
            ), "[[", 1)))
        
                sign_bi_tri <-
                    as.dist(binary_triangular_matrix(group = sapply(strsplit(
                        rownames(dist_tri), "_"
                    ), "[[", 3)))
                
                rect_var <-
                    cbind(as.dist(dist_tri), freq_bi_tri, sign_bi_tri)
                
                colnames(rect_var) <-
                    c("dtw_dist", "frequency", "sign")
                
                dtw_wv_mod <-
                    MRM2(
                        formula = dtw_dist ~ components + sign,
                        nperm = 10000,
                        mat = rect_var
                    )
            } else 
                dtw_wv_mod <- NULL
            return(dtw_wv_mod) 
        })
        
        names(mods) <- paste0("snr:", y$target.snr[1], "_", comps)
        
        mods <- mods[!sapply(mods, is.null)]        
        
        return(mods)
    })

saveRDS(
    dtw_wv_mod_list,
    "./data/processed/matrix_correlation_dtw_distance_varying_snr_by_components.RDS"
)

```

Discriminating Schroeder's by phase grouped by number of components:
```{r, fig.cap = "Effect sizes for phase by signal-to-noise ratio and number of components. Dotted line shows the cutoff for statistical significance.", out.width="100%"}
mods <- readRDS(
    "./data/processed/matrix_correlation_dtw_distance_varying_snr_by_components.RDS"
)

estimates_list <- lapply(mods, function(y) {
    estimates <- do.call(rbind, lapply(seq_along(y), function(x) {
        Y <- data.frame(y[[x]]$coef[-1,])
        # Y$rel_coef <- Y[, 1] / max(Y[, 1])
        Y$rel_coef <- Y[, 1]
        Y$mod <- names(y)[x]
        Y$predictor <- rownames(Y)
        Y$comps <- strsplit(names(y)[x], "_")[[1]][2]
        Y$comps <- strsplit(Y$comps, ":")[[1]][2]
        names(Y) <- c("coef", "p", "rel_coef", "model", "predictor", "comps")
        Y$snr <- gsub("_", "", substr(names(y)[x], 0, 6))

        return(Y)
    }))
    
    estimates$rel_coef <-
        ifelse(estimates$p < 0.05, estimates$rel_coef, 0)
    estimates$signif <-
        ifelse(estimates$p < 0.05, "p < 0.05", "p >= 0.05")
    
    return(estimates)
})
estimates <- do.call(rbind, estimates_list)

estimates$snr <- as.numeric(substr(estimates$snr, 5, nchar(estimates$snr)))

estimates$comps <- factor(estimates$comps, levels =  unique(as.numeric(estimates$comps)))

rownames(estimates) <- 1:nrow(estimates)

coef_by_signif <- aggregate(coef ~ signif, data = estimates[estimates$predictor == "sign",], FUN = range)

ggplot(estimates[estimates$predictor == "sign",], aes(y = coef, x = snr, color = comps)) +
    geom_line(linewidth = 1.6) +
    labs(x = "Signal-to-noise ratio", y = "Effect size when discriminating sign", color = "Components") + 
    scale_color_viridis_d(alpha = 0.7, begin = 0.2, end = 0.8) +
    geom_hline(yintercept = mean(coef_by_signif[,2][1, 1], coef_by_signif[,2][2, 2]), lty = 2, color = "gray") +
    theme_classic()
```

Discriminating Schroeder's by frequency grouped by number of components:
```{r, fig.cap = "Effect sizes for frequency by signal-to-noise ratio and number of components.", out.width="100%"}

ggplot(estimates[estimates$predictor == "frequency",], aes(y = coef, x = snr, color = comps)) +
    geom_line(linewidth = 1.6) +
    labs(x = "Signal-to-noise ratio", y = "Effect size when discriminating frequency", color = "Components") + 
    scale_color_viridis_d(alpha = 0.7, begin = 0.2, end = 0.8) +
      theme_classic()

```

##### On single Schroeders
```{r, eval = FALSE}

cor_snr_list <-
    readRDS("./data/processed/waveform_correlation_adjusted_snr_single_schroeders_white_noise.RDS")
    
adj_snr_schroeder1 <- readRDS("./data/processed/200ms_schroeders_adjusted_snr_white_noise.RDS")[[1]]

adj_snr_schroeder1$sound.id <- gsub("f0:f0 ", "f0:", adj_snr_schroeder1$sound.id)

    
cor_mod_list <-
    warbleR:::pblapply_wrblr_int(names(cor_snr_list), cl = 20, function(y) {
        
        x <- cor_snr_list[[y]]
        target_snr <- "snr:30"
        
        x$schr1 <- sapply(strsplit(x$schr1, "_"), function(x) paste(x[2], x[3], substr(x[4], 0, 1),sep = "_"))
        x$schr2 <- sapply(strsplit(x$schr2, "_"), function(x) paste(x[2], x[3], substr(x[4], 0, 1),sep = "_"))
        x$cor <- x$cor * -1
        
        dist_tri <- PhenotypeSpace::rectangular_to_triangular(x)
        
        freq_bi_tri <-
            as.dist(binary_triangular_matrix(group = sapply(strsplit(
                rownames(dist_tri), "_"
            ), "[[", 1)))
        
        comp_bi_tri <-
            as.dist(binary_triangular_matrix(group = gsub(
                "_n|_p", "", sapply(strsplit(rownames(dist_tri), "_"), "[[", 2)
            )))
        
        sign_bi_tri <-
            as.dist(binary_triangular_matrix(group = sapply(strsplit(
                rownames(dist_tri), "_"
            ), "[[", 3)))
        
        rect_var <-
            cbind(as.dist(dist_tri), freq_bi_tri, comp_bi_tri, sign_bi_tri)
        
        colnames(rect_var) <-
            c("cor", "frequency", "components", "sign")
        
        cor_wv_mod <-
            MRM2(
                formula = cor ~ frequency + components + sign,
                nperm = 10000,
                mat = rect_var
            )
        
        return(cor_wv_mod)
    })

names(cor_mod_list) <- names(cor_snr_list)

saveRDS(
    cor_mod_list,
    "./data/processed/matrix_regression_waveform_correlation_varying_snr_single_schroeder_white_noise.RDS"
)

```


```{r, fig.cap = "Effect sizes by signal-to-noise ratio and predictor (color intensity shows effect size magnitude relative to the highest effect size within the model).", out.width="100%", fig.width=6, fig.height=4}
mods <- readRDS(
    "./data/processed/matrix_regression_waveform_correlation_varying_snr_single_schroeder_white_noise.RDS"
)


estimates_wf_wn_stnd <- do.call(rbind, lapply(seq_along(mods), function(x) {
  Y <- data.frame(mods[[x]]$coef[-1, ])
  # Y$rel_coef <- Y[, 1] / max(Y[, 1])
  Y$rel_coef <- Y[, 1] 
  Y$predictor <- rownames(Y)
  Y$model <- as.numeric(gsub("snr:", "", names(mods)[x]))
  names(Y) <- c("coef", "p", "rel_coef", "predictor", "model")
  return(Y)
}))

estimates_wf_wn_stnd$rel_coef <- ifelse(estimates_wf_wn_stnd$p < 0.05, estimates_wf_wn_stnd$rel_coef, 0)
estimates_wf_wn_stnd$signif <- ifelse(estimates_wf_wn_stnd$p < 0.05, "p < 0.05", "p >= 0.05")
estimates_wf_wn_stnd$signif2 <- ifelse(estimates_wf_wn_stnd$p < 0.05, "*", "")

estimates_wf_wn_stnd$model_f <- factor(estimates_wf_wn_stnd$model, levels = 1:30)

ggplot(estimates_wf_wn_stnd, aes(x = predictor, y = model_f, fill = rel_coef)) +
  geom_tile() +
  coord_equal() + 
    scale_fill_gradient2(
low = viridis(10)[3], high = viridis(10)[7],
    guide = "none"
  ) +
  geom_text(aes(label = signif2, color = signif), size = 3) +
  scale_color_manual(values = c("black", "gray"))+
    labs(y = "Signal-to-noise ratio", x = "Predictor", color = "P value") +
  theme_classic() +
  theme(axis.text.x = element_text(
    color = "black",
    size = 7, angle = 30, vjust = 0.8, hjust = 0.8
  )) + coord_flip()


estimates_wf_wn_stnd$model <- as.numeric(estimates_wf_wn_stnd$model)
```

```{r, fig.cap = "Effect sizes by signal-to-noise ratio and predictor waveform correlation", out.width="100%"}

coef_by_signif <- aggregate(coef ~ signif, data = estimates_wf_wn_stnd, FUN = range)

ggplot(estimates_wf_wn_stnd, aes(y = coef, x = model, color = predictor, lty = predictor)) +
    geom_line(linewidth = 1.6) +
    labs(x = "Signal-to-noise ratio", y = "Effect size") + 
    scale_color_viridis_d(alpha = 0.7, begin = 0.2, end = 0.8) +
    geom_hline(yintercept = mean(coef_by_signif[,2][1, 1], coef_by_signif[,2][2, 2]), lty = 2, color = "gray") +
    theme_classic()

    
```

###### By frequency
```{r, eval = FALSE}

cor_snr_list <-
    readRDS(
            "./data/processed/matrix_regression_waveform_correlation_varying_snr_single_schroeder_white_noise.RDS"
        )
adj_snr_schroeder1 <- readRDS("./data/processed/200ms_schroeders_adjusted_snr_white_noise.RDS")[[1]]


cor_snr_list <- lapply(seq_along(cor_snr_list), function(x) {
    Y <- cor_snr_list[[x]]
    Y$target.snr <- gsub("snr:", "", names(cor_snr_list)[x])
    return(Y)
    })

adj_snr_schroeder1$sound.id <- gsub("f0:f0 ", "f0:", adj_snr_schroeder1$sound.id)

cor_mod_list <-
    warbleR:::pblapply_wrblr_int(cor_snr_list, cl = 1, function(y) {
        
        freqs <- unique(substr(sapply(y[,1], function(x) adj_snr_schroeder1$sound.id[adj_snr_schroeder1$sound.files == x])
    , 0, 6))

        mods <- lapply(1:length(freqs), function(i){
            
            y$schr1 <- sapply(y$schr1, function(x) adj_snr_schroeder1$sound.id[adj_snr_schroeder1$sound.files == x])
            y$schr2 <- sapply(y$schr2, function(x) adj_snr_schroeder1$sound.id[adj_snr_schroeder1$sound.files == x])

            
            # extract only those with the same freq
            x <- y[grepl(paste(freqs[i], collapse = "|"), y$schr1) & grepl(paste(freqs[i], collapse = "|"), y$schr2),]
            
            target_snr <- x$target.snr
            x$target.snr <- NULL
            x$cor <- 1- x$cor
            
            dist_tri <- PhenotypeSpace::rectangular_to_triangular(x)
            
            if (nrow(dist_tri) > 2){
                comp_bi_tri <-
                    as.dist(binary_triangular_matrix(group = gsub(
                        "_n|_p", "", sapply(strsplit(rownames(dist_tri), "_"), "[[", 2)
                    )))
                
                sign_bi_tri <-
                    as.dist(binary_triangular_matrix(group = sapply(strsplit(
                        rownames(dist_tri), "_"
                    ), "[[", 3)))
                
                rect_var <-
                    cbind(as.dist(dist_tri), comp_bi_tri, sign_bi_tri)
                
                colnames(rect_var) <-
                    c("dtw_dist", "components", "sign")
                
                cor_mod <-
                    MRM2(
                        formula = dtw_dist ~ components + sign,
                        nperm = 10000,
                        mat = rect_var
                    )
            } else 
                cor_mod <- NULL
            return(cor_mod) 
        })
        
        names(mods) <- paste0("snr:", y$target.snr[1], "_", freqs)
        
        mods <- mods[!sapply(mods, is.null)]        
        
        return(mods)
    })

saveRDS(
    cor_mod_list,
    "./data/processed/matrix_correlation_waveforme_correlatione_varying_snr_by_frequency_white_noise_single_schroeder.RDS"
)

```


### Measure linear-frequency spectrogram cross-correlation
```{r, eval = FALSE}

adj_snr_schroeder <- readRDS("./data/processed/200ms_schroeders_adjusted_snr_white_noise.RDS")

xc_list <- lapply(adj_snr_schroeder, function(schroeders){
  
        print(schroeders$target.snr[1])  
        
    xc <- cross_correlation(schroeders, ovlp = 90, parallel = 20, wn = "hamming")

    })

names(xc_list) <- paste0("snr:", sapply(adj_snr_schroeder, function(x) x$target.snr[1]))

saveRDS(xc_list, "./data/processed/fourier_cross_correlation_varying_snr_200ms_schroeders_white_noise.RDS")


beepr::beep(2)


```

```{r}

xc_list <-
    readRDS("./data/processed/fourier_cross_correlation_varying_snr_200ms_schroeders_white_noise.RDS")
    
adj_snr_schroeder1 <- readRDS("./data/processed/200ms_schroeders_adjusted_snr_pink_noise.RDS")[[1]]

adj_snr_schroeder1$sound.id <- gsub("f0:f0 ", "f0:", adj_snr_schroeder1$sound.id)
    
xc_mod_list <-
    warbleR:::pblapply_wrblr_int(seq_along(xc_list), cl = 20, function(x) {

        X <- xc_list[[x]]
                
        # x$dist <- scale(x$dist)
        target_snr <- gsub("snr:", "", names(xc_list)[x])

        colnames(X) <- sapply(gsub("-1$", "", colnames(X)), function(x) adj_snr_schroeder1$sound.id[adj_snr_schroeder1$sound.files == x])
rownames(X) <- sapply(gsub("-1$", "", rownames(X)), function(x) adj_snr_schroeder1$sound.id[adj_snr_schroeder1$sound.files == x])        
        # convert to distance
        X <- 1 - X

        # cor_tri <- PhenotypeSpace::rectangular_to_triangular(x)
        
        freq_bi_tri <-
            as.dist(binary_triangular_matrix(group = sapply(strsplit(
                rownames(X), "_"
            ), "[[", 1)))
        
        comp_bi_tri <-
            as.dist(binary_triangular_matrix(group = gsub(
                "_n|_p", "", sapply(strsplit(rownames(X), "_"), "[[", 2)
            )))
        
        sign_bi_tri <-
            as.dist(binary_triangular_matrix(group = sapply(strsplit(
                rownames(X), "_"
            ), "[[", 3)))
        
        rect_var <-
            cbind(as.dist(X), freq_bi_tri, comp_bi_tri, sign_bi_tri)
        
        colnames(rect_var) <-
            c("xcor", "frequency", "components", "sign")
        
        dtw_wv_mod <-
            MRM2(
                formula = xcor ~ frequency + components + sign,
                nperm = 10000,
                mat = rect_var
            )
        
        return(dtw_wv_mod)
    })

names(xc_mod_list) <- names(xc_list)

saveRDS(
    xc_mod_list,
    "./data/processed/matrix_regression_cross_correlation_varying_snr_white_noise.RDS"
)
```


Discriminating Schroeder's by phase grouped by number of components:
```{r, fig.cap = "Effect sizes for phase by signal-to-noise ratio and number of components. Dotted line shows the cutoff for statistical significance.", out.width="100%"}
mods <- readRDS(
    "./data/processed/matrix_regression_cross_correlation_varying_snr_white_noise.RDS"
)

estimates_xc_wn <- do.call(rbind, lapply(seq_along(mods), function(x) {
  Y <- data.frame(mods[[x]]$coef[-1, ])
  # Y$rel_coef <- Y[, 1] / max(Y[, 1])
  Y$rel_coef <- Y[, 1] 
  Y$predictor <- rownames(Y)
  Y$model <- as.numeric(gsub("snr:", "", names(mods)[x]))
  names(Y) <- c("coef", "p", "rel_coef", "predictor", "model")
  return(Y)
}))

estimates_xc_wn$rel_coef <- ifelse(estimates_xc_wn$p < 0.05, estimates_xc_wn$rel_coef, 0)
estimates_xc_wn$signif <- ifelse(estimates_xc_wn$p < 0.05, "p < 0.05", "p >= 0.05")
estimates_xc_wn$signif2 <- ifelse(estimates_xc_wn$p < 0.05, "*", "")

estimates_xc_wn$model_f <- factor(estimates_xc_wn$model, levels = 1:30)

ggplot(estimates_xc_wn, aes(x = predictor, y = model_f, fill = rel_coef)) +
  geom_tile() +
  coord_equal() + 
    scale_fill_gradient2(
low = viridis(10)[3], high = viridis(10)[7],
    guide = "none"
  ) +
  geom_text(aes(label = signif2, color = signif), size = 3) +
  scale_color_manual(values = c("black", "gray"))+
    labs(y = "Signal-to-noise ratio", x = "Predictor", color = "P value") +
  theme_classic() +
  theme(axis.text.x = element_text(
    color = "black",
    size = 7, angle = 30, vjust = 0.8, hjust = 0.8
  )) + coord_flip()


estimates_xc_wn$model <- as.numeric(estimates_xc_wn$model)
```

```{r, fig.cap = "Effect sizes by signal-to-noise ratio and predictor waveform correlation", out.width="100%"}

coef_by_signif3 <- aggregate(coef ~ signif, data = estimates_xc_wn, FUN = range)

ggplot(estimates_xc_wn, aes(y = coef, x = model, color = predictor, lty = predictor)) +
    geom_line(linewidth = 1.6) +
    labs(x = "Signal-to-noise ratio", y = "Effect size") + 
    scale_color_viridis_d(alpha = 0.7, begin = 0.2, end = 0.8) +
    theme_classic()

    
```


#### Only phase
```{r, fig.cap = "Effect sizes by signal-to-noise ratio and predictor.", out.width="100%"}

ggplot(estimates_xc_wn[estimates_xc_wn$predictor == "sign", ], aes(y = abs(coef), x = model, color = predictor, lty = predictor)) +
    geom_line(linewidth = 1.6) +
    geom_smooth() +
    labs(x = "Signal-to-noise ratio", y = "Effect size") + 
    scale_color_viridis_d(alpha = 0.7, begin = 0.2, end = 0.8) +
    geom_hline(yintercept = 0, lty = 2, color = "gray") +
    theme_classic() 


```

# Combined results plot

```{r}

estimates_wf_wn_stnd$method <- "waveform correlation standard"
estimates_wf_wn$method <- "waveform correlation sliding window"
estimates_dtw_wn_stnd$method <- "waveform DTW standard"
estimates_dtw_wn$method <- "waveform DTW sliding window"
# estimates_xc_wn$method <- "cross-correlation"

estims <- rbind(estimates_wf_wn, estimates_dtw_wn, estimates_wf_wn_stnd, estimates_dtw_wn_stnd)

coef_by_signif2 <- aggregate(coef ~ signif + method, data = estims, FUN = range)

# is this
ltypes <- ifelse(as.numeric(factor(estims$method[estims$predictor == "sign"])) %%2 == 0, 1, 2)

ests <- estims[estims$predictor == "sign", ]

ests$type <- ifelse(grepl("standard", ests$method), "point estimate", "sliding window") 
ests$meth <- ifelse(grepl("DTW", ests$method), "waveform DTW", "waveform correlation") 


ggplot(ests, aes(y = coef, x = model, color = type, lty = meth)) +
    geom_line(linewidth = 1.6) +
    geom_smooth(se = TRUE, show.legend  = FALSE) +
    labs(x = "Signal-to-noise ratio (dB)", y = "Phase effect size", color = "Approach", lty = "Method") + 
    scale_color_viridis_d(alpha = 0.7, begin = 0.3, end = 0.9, option = "G") +
    xlim(c(1, 30)) +
    geom_hline(yintercept = 0, lty = 2, color = "gray") +
    theme_classic(base_size = 20)  +
    scale_x_continuous( expand = c(0, 0))


# ggplot(estims[estims$predictor == "sign", ], aes(y = abs(coef), x = model, color = method)) +
#     geom_line(linewidth = 1.6) +
#     # geom_smooth(se = FALSE) +
#     labs(x = "Signal-to-noise ratio", y = "Phase\neffect size") + 
#     scale_color_viridis_d(alpha = 0.7, begin = 0.2, end = 0.8) +
#     geom_hline(yintercept = 0, lty = 2, color = "gray") +
#     theme_classic()  +
#     scale_x_continuous( expand = c(0, 0), limits = c(0, 10)) 
# 

```


<!-- light green box -->

<div class="alert alert-success">

# Takeaways

- 

</div>

&nbsp; 
 
 <!-- add packages used, system details and versions  -->
 
<font size="4">Session information</font>

```{r session info, echo=F}

sessionInfo()
```


